First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-12-13 MY_PUBLICATIONS/PRL/draft_v2/body.tex
update

\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes\cite{hodo_techreport} (scintillator arrays) used for triggering,

@@

measured on this experiment. As a result one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
At these forward angles and large momentum transferred to the proton, the additional process in which the recoiling neutron is struck by the vitrual photon is suppressed. \\
\indent Hydrogen elastic ($^{1}H(e,e'p)$) data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo

@@

For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has also been calculated. The ratio between the calculated cross section at the averaged kinematics and the averaged
cross section for this bin has also been determined and used to compare theoretical models to the experimental cross sections. The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\

@@

\includegraphics[scale=0.45]{../prl_plots/PRL_plot1.pdf}

@@

(GeV/c)$^{2}$. The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig1}
provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{Sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible. As a result, our data at larger recoil angles
is statistically limited. \\
\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the
momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
\indent In Fig. \hyperref[fig:fig1]{1(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig1]{1(a)}.
For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\

>>>>

\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four scintillator planes\cite{hodo_techreport} used for triggering,

@@

measured on this experiment. As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
At these forward angles and large momentum transferred to the proton, the additional process in which the neutron is struck by the virtual photon is suppressed. \\
\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo

@@

For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has also been calculated and used in the bin centering correction factor defined as:
$f_{bc} \equiv \sigma_{avg.kin} / \bar{\sigma}$, where $\sigma_{avg.kin}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross
section averaged over the kinematic bin. The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\

@@

\includegraphics[scale=0.50]{../prl_plots/PRL_plot1.pdf}

@@

(GeV/c)$^{2}$. The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan). The data is compared to theoretical reduced
cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
\indent At recoil angles $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], all models agree and are sensitive to momentum distributions up to $p_{r}\sim$300 MeV/c. Beyond $p_{r}\sim$300 MeV/c, FSIs become
dominant and all models exhibit a similar behaviour which obscures any possibility of extracting the momentum distributions at these angles. At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$ shown in
Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)}, all models are sensitive to momentum distributions to some extent beyond $300$ MeV/c before FSIs start to appear. The Paris and AV18 calculations
exhibit a similar behaviour in the momentum distributions as opposed to the CD-Bonn calculation, where FSIs start to show up earlier than the other models predict.

%The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig1}
%provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
%was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
%\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
%smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{Sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
%This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible. As a result, our data at larger recoil angles
%is statistically limited. \\
%\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the
%momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
%NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
%\indent In Fig. \hyperref[fig:fig1]{1(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
%to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
%a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig1]{1(a)}.
%For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\

### 2019-12-13 MY_PUBLICATIONS/PRL/draft_v2/introduction.tex
update

Being the only two-nucleon bound system, the deuteron serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently

@@

electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA the virtual photon couples to
the proton which is subsequently ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction

@@

modulus-squared of the FSI amplitude (rescattering term). This cancellation results in only the PWIA term remaining in the deuteron cross section and is expected to occur at netron recoil angles $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$,
opening a kinematic window to study the short-range structure of the deuteron. \\

@@

the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented confirmed the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}. Most importantly, for recoil
neutron momentum bins, $p_{r}=0.4\pm0.02$ and $0.5\pm0.02$ GeV/c, the ratio was found to be $R\sim1$ for $35^{o}\leq \theta_{nq}\leq45^{o}$ indicating a reduced sensitivity of the experimental
cross-section to FSIs. This kinematic window allowed for the first time the extraction of momentum distributions for neutron recoil momenta up to $p_{r}\sim$550 MeV/c. \\
\indent The experiment presented on this Letter takes advantage of the kinematic window previosuly found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measurements

>>>>

The deuteron is the only two-nucleon bound system. Therefore, it serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently

@@

electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA, the virtual photon couples to
the proton which is subsequently ejected from the nucleus without further interaction with the recoiling neutron. The neutron carries a momentum equal in magnitude but opposite in direction

@@

modulus-squared of the FSI amplitude (rescattering term). This cancellation results in only the PWIA term remaining in the deuteron cross section and is expected to occur at netron recoil angles $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$. \\

@@

the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented saw agreement in shape with the angular distributions in Hall B\cite{PhysRevLett.98.262502} with FSI peaking at $\theta_{nq}\sim70^{o}$. With the increased statistics in Hall A, a direct comparison of the momentum distributions between data and theory could be made for specific $\theta_{nq}$ bins. For the first time, at $\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, theoretical models showed a sensitivity to the NN-potential used in the deuteron wavefunction that was not obscured by FSI contributions to the cross section data.\\
\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measurements

### 2019-12-13 MY_PUBLICATIONS/PRL/draft_v2/prl.tex
update

%% ****** Start of file template.aps ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.0 of REVTeX, August 2001
%%
%%
%%   Copyright (c) 2001 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,preprint]{revtex4-2}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 01 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

>>>>

%% ****** Start of file template.aps ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.0 of REVTeX, August 2001
%%
%%
%%   Copyright (c) 2001 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 02 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
